When are Fuzzy Extractors Possible?

### 2015-01-05 info-bounds/FuzzyExtPossibility.tex
working on reviewer comments

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{
Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston University and MIT Lincoln Laboratory.}  \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.  Pennsylvania State University; work performed while at Boston University's Hariri Institute for Computing and RISCS Center, and Harvard University's
``Privacy Tools'' project.}}
}
\begin{document}
\maketitle

@@

High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required. Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy. In this work, we ask: \emph{is fuzzy min-entropy sufficient to build information-theoretic fuzzy extractors?} 
%\lnote{Or it seems sufficient under strong computational assumptions and, under weaker assumptions, in the interactive setting.}  
%\lnote{may be use``analyzing this quantity may be more fruitful than analyzing min-entropy and error-tolerance separately''}

@@

\paragraph{Fuzzy Min-Entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.  Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$.

Superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition). 
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

@@

We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W)=\Hoo(W)$, because all points in $W$ are distance at least $t$ apart. Our proof relies on high dimensionality of $W$ and on perfect correctness of the $\rep$ procedure.

@@

On the other hand, there is a family of sources with superlogarithmic $\Hfuzz(W)=\Hoo(W)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}). The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).

\subsection{Our Techniques}

@@

\paragraph{Techniques for Negative Results for Distribution Families}
We construct a family of distributions $\mathcal{W}$ and prove impossibility for a uniformly random $W\in \mathcal{W}$~(instead of proving impossibility for a worst-case $W$).
We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
the adversary knows $W$.   To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.

@@

\paragraph{Correlated rather than close readings}
A different model for the problem of key derivation from noisy sources does not explicitly consider the distance between $w$ and $w'$, but rather views $w$ and $w'$ as samples of drawn from a correlated pair of random variables.   This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.

@@

\paragraph{Organization} The remainder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor for every known distribution with fuzzy min-entropy.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results  for families of distributions for secure sketches and fuzzy extractors, respectively.

@@

The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $w$} is the set of all points within radius $t$, that is, $B_t(w) = \{w'| \dis(w, w')\leq t\}$.  If the size of a ball in a metric space does not depend on $w$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(w,w') = \{i | w_i \neq w'_i\}$ where $\mathcal{Z}$ is some alphabet.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_\kappa$ denotes the uniformly  distributed random variable on $\{0,1\}^\kappa$.  Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience. A \emph{negligible} function $\ngl(n)$ is one that decreases faster than any positive inverse polynomial as $n\rightarrow \infty$.

@@

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}
\noindent
Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):
\begin{proposition}
\label{prop:fuzz necessary}
Let $W$ be a distribution over $(\mathcal{M}, \dis)$ and let $n= \log |\mathcal{M}|$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
 with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
\noindent
There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy. % We now describe the known distribution setting.

%\subsection{Known Distribution Algorithms}
%\label{sec:known distributions def}
%To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.  
%We call an algorithm with complete information on $W$ \emph{known distribution}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):
%
%\begin{definition}
%Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{known distribution %secure sketch} with error $\delta$ if the correctness and security properties hold for the distribution $W$.  That is, 
%\begin{enumerate}
%\item \emph{Correctness:} 
%$
%\forall w\in \supp(W)$, $\forall w' \in\mathcal{M}| \dis(w,w')\le t$, $\Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$\\
%Correctness is guaranteed only for the support of $W$.
%\item \emph{Security:} $\Hav(W|\sketch(W))\geq \tilde{m}$.
%\end{enumerate}
%\end{definition}
%$(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  We assume known distribution algorithms are \emph{inefficient}.  Finding a natural model of specifying distributions that allows for efficient~(yet generic) known distribution constructions of sketches and extractors is an interesting problem.

@@

Denote the largest number of points in a ball of radius $t$ in the support of $W$ as $\beta_{t} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|$.   For flat distributions, the weight of this maximum-probability ball (which determines $\Hfuzz(W)$ by \defref{def:fuzzy min-ent}) is proportional to the number of points in it.  More precisely, 
\begin{align}
\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} \right|\cdot \Pr[W=w]\right) \nonumber \\
&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in \supp(W) \wedge \dis(w, w')\le t\}| \cdot 2^{-\Hoo(W)}\right) \nonumber \\
&= \Hoo(W) -\log \beta_{t}.\label{eq:fuzz for flat}
\end{align}

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{2.5in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item Sample $K\leftarrow \mathcal{K}$.
\item Set $p = F(K, w), K$.
\end{enumerate}
\vspace{.3in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', p = y, K)$
\item Let $W^* = \{w \in \supp(W) | \dis(w, w')\le t\}$.
\item For $w^*\in W^*$, if $F(K, w^*) = y$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $W$ be a distribution with $\Hoo(W)= m$.  Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions.  Define $\sketch_W, \rec_W$ as: 
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. Set $p=0,w$.
\item Else
\begin{enumerate}
\item Find $i$ such that $\Pr[W=w]\in L_i$.
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $ss =1,  i, F_i(K, w), K$.
\end{enumerate}
\end{enumerate}
\vspace{.4in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss)$
\item If $ss_0 = 1$, output $ss_{1,..., |y|}$.
\item Else
\begin{enumerate}
\item Parse $(i, y, K) = ss_{1,..., |y|}$.
\item $W^* = \{w \in \supp(W) | \dis(w, w')\le t \\\, \, \, \wedge \Pr[W=w]\in L_i\}$.
\item For $w^*\in W^*$, if $F_i(K, w^*) = z$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\noindent
We extend our notation for the maximum likelihood ball to the leveled case.  Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.  That is,
\[
\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
\]

@@

\end{theorem}
We provide a proof in \apref{sec:proof of layered hashing}.  The main idea is to show that an adversary that knows the level of $w$ cannot perform much better than an adversary without this information.

@@

\noindent
In our positive results we considered an arbitrary finite metric space.  The relevant parameters were the size of balls and the size of the metric space.  Our negative results are specific to the Hamming metric.
\section{Impossibility of Secure Sketches for a Family with $\Hfuzz$}
\label{sec:family of dist}

@@

@@

\section{Proof of \thref{thm:layered hashing}}
\label{sec:proof of layered hashing}
\begin{proof}
Throughout the proof we assume that $\ell = n$ is the number of levels.  The proof can be carried out for an arbitrary $\ell$ but it leads to a complicated theorem statement.

@@

Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.  The size of $W^*$ is at most $\beta_{t,i}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  The probability that another element $w^*$ matches the hash is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{\beta_{t,i}-1}{|R_i|} = \delta
\end{align*}
The inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $\beta_{t,i}$.

>>>>

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{
Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston
  University and MIT Lincoln Laboratory.}  \and Leonid
Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.}
\and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.
  Pennsylvania State University. This work performed while visiting Boston
  University's Hariri Institute for Computing.}}
}
\begin{document}
\maketitle

@@

High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required. Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy. In this work, we ask: \emph{is fuzzy min-entropy sufficient to build information-theoretic fuzzy extractors?}

\bnote{fuzzy min-entropy measures ideal security ... similar to encryption/etc.}
\bnote{should introduce the idea of distributional uncertainty...very important for us}
%\lnote{Or it seems sufficient under strong computational assumptions and, under weaker assumptions, in the interactive setting.}  
%\lnote{may be use``analyzing this quantity may be more fruitful than analyzing min-entropy and error-tolerance separately''}

@@

\paragraph{Fuzzy Min-Entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.  Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$.
\bnote{should note that fuzzy min-entropy is the ideal security, measures how an adversary would do with oracle access, goal is to implement this oracle}

Superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition). 
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}. 
\bnote{introduce distributional uncertainty here}

@@

We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}_Z$ such that not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}_Z$.  We emphasize that each distribution $W_z\in \mathcal{W}_Z$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W_z)=\Hoo(W_z)$, because all points in $W_z$ are distance at least $t$ apart. Our proof relies on high dimensionality of each $W_z$ and on perfect correctness of the $\rep$ procedure.

@@

On the other hand, there is a family of sources, $\mathcal{W}_Z$, where each element has $\Hfuzz(W_z)=\Hoo(W_z) = \omega(\log n)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}). The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).

\bnote{asked to discuss implications of our negative results}
\bnote{can we reframe the paper as the cost of distributional uncertainty?}
\bnote{compare to current constructions?}
\subsection{Our Techniques}

@@

\paragraph{Techniques for Negative Results for Distribution Families}
We construct a family of distributions $\mathcal{W}_Z$ and prove impossibility for a uniformly random $W_z \leftarrow \mathcal{W}_Z$~(instead of proving impossibility for a worst-case $W_z$).
We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W_z\leftarrow \mathcal{W}_Z$ and $w\leftarrow W_z$), while
the adversary knows $W_z$.   To exploit the asymmetry, we construct $\mathcal{W}_Z$ so that conditioning on the knowledge of $W_z$~(the outcome $z$) reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.

@@

\paragraph{Correlated rather than close readings}
A different model for the problem of key derivation from noisy sources does not explicitly consider the distance between $w$ and $w'$, but rather views $w$ and $w'$ as samples of drawn from a correlated pair of random variables.   This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.  We compare our positive results to these characterizations in \apref{sec:corr variables}.  To the best of our knowledge, prior results on correlated random variables are in the known distribution setting, we are unaware of works that consider security for families of distributions.

@@

\paragraph{Organization} The remainder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor for each known distribution with fuzzy min-entropy.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results  for families of distributions for secure sketches and fuzzy extractors, respectively.

@@

The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
%For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.
For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $w$} is the set of all points within radius $t$, that is, $B_t(w) = \{w'| \dis(w, w')\leq t\}$.  If the size of a ball in a metric space does not depend on $w$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(w,w') = \{i | w_i \neq w'_i\}$ where $\mathcal{Z}$ is some alphabet.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_\kappa$ denotes the uniformly  distributed random variable on $\{0,1\}^\kappa$.  Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience. A \emph{negligible} function $\ngl(n)$ is one that decreases faster than any positive inverse polynomial as $n\rightarrow \infty$.

@@

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}
\noindent
\bnote{Should note this is the ideal security of a noisy source, both in the interactive/non-interactive settings}
Fuzzy min-entropy is a necessary condition for security~(proof in \apref{sec:proof fuzz necessary}):
\begin{proposition}
\label{prop:fuzz necessary}
Let $W$ be a distribution over $(\mathcal{M}, \dis)$ and let $n= \log |\mathcal{M}|$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
 with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
\noindent
There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
Our goal is to provide a superlogarithmic length key when provided with superlogarithmic fuzzy min-entropy.

\bnote{I feel we can provide a more general results than this one.  Helpful?}

@@

Denote the largest number of points in a ball of radius $t$ in the support of $W$ as $\beta_{t} = \max_{w'\in\M} |\{w | w\in \supp(W) \wedge \dis(w ,w')\le t\}|$.   For flat distributions, the weight of the maximum-probability ball (which determines $\Hfuzz(W)$ by \defref{def:fuzzy min-ent}) is proportional to the number of points in it.  More precisely, 
\begin{align}
\Hfuzz(W) &= -\log \left(\max_{w' \in \mathcal{M}} \left| \{w | w\in \supp(W) \wedge \dis(w, w')\le t\} \right|\cdot \Pr[W=w]\right) \nonumber \\
&= -\log\left( \max_{w' \in \mathcal{M}} |\{w | w\in \supp(W) \wedge \dis(w, w')\le t\}| \cdot 2^{-\Hoo(W)}\right) \nonumber \\
&= \Hoo(W) -\log \beta_{t}.\label{eq:fuzz for flat}
\end{align}

@@

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{2.5in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item Sample $K\leftarrow \mathcal{K}$.
\item Set $ss = F(K, w), K$.
\end{enumerate}
\vspace{.3in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss =( y, K))$
\item Let $W^* = \{w \in \supp(W) | \dis(w, w')\le t\}$.
\item For $w^*\in W^*$, if $F(K, w^*) = y$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $W$ be a distribution with $\Hoo(W)= m$.  Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell-1$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions.  Define $\sketch_W, \rec_W$ as: 
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. Set $ss=1,w$.
\item Else
\begin{enumerate}
\item Find $i$ such that $\Pr[W=w]\in L_i$.
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $ss =0,  i, F_i(K, w), K$.
\end{enumerate}
\end{enumerate}
\vspace{.4in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss)$
\item If $ss_0 = 1$, output $ss_{1,..., |y|}$.
\item Else
\begin{enumerate}
\item Parse $(i, y, K) = ss_{1,..., |y|}$.
\item $W^* = \{w \in \supp(W) | \dis(w, w')\le t \\\, \, \, \wedge \Pr[W=w]\in L_i\}$.
\item For $w^*\in W^*$, if $F_i(K, w^*) = z$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\noindent

@@

\end{theorem}
We provide a proof in \apref{sec:proof of layered hashing}.  The main idea is to show that an adversary that knows the level of $w$ cannot perform much better than an adversary without this information.  \bnote{this sentence isn't helpful, provide better intuition}

@@

\noindent
In our positive results we considered an arbitrary finite metric space.  The relevant parameters were the size of balls and the size of the metric space.  Our negative results are specific to the Hamming metric.

\section{Impossibility of Secure Sketches for a Family with $\Hfuzz$}
\label{sec:family of dist}

@@

\section{Key Derivation from Correlated Random Variables}
\label{sec:corr variables}

In this work, we consider two draws from some physical source whose distance was bounded according to some metric space.
Instead of considering $w, w'$ that have bounded distance, we can treat $W, W'$ as a pair of correlated random variables.  
  Renner and Wolf~\cite{DBLP:conf/asiacrypt/RennerW05} study this setting, firsting consider information-reconciliation and privacy amplification separately.  They show that $\Hoo(W)$ is a necessary and sufficient condition for privacy amplification.\footnote{The results of Renner and Wolf use smooth notions of entropy.  A random variable has smooth entropy if it is statistically close to a distribution with true entropy. We describe their results in the terminology of non smooth entropy.}  Second, they show that the length of $p$ must grow with the worst case number of possible outcomes for $W$ conditioned on $W'$.\footnote{This result also uses a smooth notion of entropy.  We describe the non smooth version for simplicity.}  That is, the length of the public value \[|p|\ge \max_{w'\in W} \log |\{w | \Pr[W=w | W'=w']>0\}|.\]

Furthermore, they show there exists a protocol with this length $p$ using optimal encoding functions.  Intuitively, the public information must describe which possible outcome for $W$ actually occurred. This result describes the maximal length of $p$ and does not argue how $p$ effects security.  It may be possible to construct a $p$ that reduces the entropy of $w$ by less than $\log |p|$.  In \secref{sec:known distributions}, we will construct schemes with variable length $p$, providing information-reconciliation for distributions where the bounds of Renner and Wolf provide no security guarantees.

Lastly, the work of Renner and Wolf shows characterize when key derivation is possible from correlated random variables~\cite[Theorem 3]{DBLP:conf/asiacrypt/RennerW05}.  Fuzzy min-entropy can be generalized to this setting.   Fuzzy extractors consider the worst case $w'$.  When considering correlated readings, it is natural to treat $W'$ as a random variable:\footnote{Fuzzy extractors are defined to require high probability of correctness for all pairs $w, w'$.  In the correlated setting, it may make sense to provide an average-case guarantee, where the probability of correctness is also over the draw of $w, w'$.  Renner and Wolf use a smoothed notion of entropy that removes the $\delta$ fraction of the probability mass of $W=w|W'=w'$ with the most points to improve parameters under such a definition.  In this work, we consider worst case correctness and use unsmoothed entropy.}

\begin{definition}
\label{def:cor fuzz min}
Let $(W, W')$ be a pair of correlated random variables.  The correlated fuzzy min-entropy of $W, W'$ is:
\[\Hcorr(W, W') = -\log \left( \max_{w'\in \supp(W')}\sum_{w\in W | \Pr[W=w|W'=w']>0} \Pr[W = w] \right).\]
\end{definition}
\noindent 
In \defref{def:fuzzy min-ent}, the sum is implicitly over $W=w|W'=w'$ since we assume any $w'$ within distance $t$ is possible.  
In \secref{sec:known distributions} we showed sufficiency  of $\Hfuzz(W)$ for key derivation from noisy sources (\defref{def:fuzzy min-ent}).

\paragraph{Connection to the characterization of~\cite{DBLP:conf/asiacrypt/RennerW05}}
Renner and Wolf characterize when it is possible to derive keys from correlated random variables~\cite[Theorem 3]{DBLP:conf/asiacrypt/RennerW05}.  They consider all possible (randomized) transforms $T, T'$ of $W, W'$ into a new pair of variables $V,V'$.  They show that \[|\key| \le \sup_{(V, V')\leftarrow (T(W), T'(W))}\left(  \Hoo(V | T') - \log \max_{v'\in V'} |\{v| \Pr[V=v|T' \wedge V'=v']>0\}|\right).\]  Furthermore, they show that there is a transformation that achieves a key of nearly this length.  The result is nonconstructive as there is no guidance on how to find the transforms $T, T'$.  Since there is no known bound on the length of $T, T'$ it is not clear how to search the transform space even with unlimited time.
\consref{cons:leveling} can be used to derive keys from correlated random variables.  The main change is to define \[W^* = \{w | \Pr[W=w | W'=w'] >0 \wedge \Pr[W=w]\in L_i\}.\]  
Our result shows if one is satisfied with obtaining a strong key when possible (our protocol has losses of $2\log 1/\epsilon + \log n+\log 1/\delta$), then a protocol is possible (and explicitly constructible) in the original space.

@@

\section{Proof of \thref{thm:layered hashing}}
\label{sec:proof of layered hashing}
\begin{proof}
Throughout the proof we assume that $\ell = n$ is the number of levels.  The proof can be carried out for an arbitrary $\ell$ but it leads to a complicated theorem statement.
We extend our notation for the maximum likelihood ball to the leveled case.  Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.  That is,
\[
\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
\]

@@

Let $W^*$ denote the set of elements of $W$ in $L_i$ within distance $t$ of $w'$.  The size of $W^*$ is at most $\beta_{t,i}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  The probability that another element $w^*$ matches the hash is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{\beta_{t,i}-1}{|R_i|} = \delta
\end{align*}
The first inequality is by union bound. The first equality follows from the universality of $F$.  The second inequality follows since the number of neighbors is bounded by $\beta_{t,i}$.
